\documentclass[letterpaper,11pt]{article}

% Packages for formatting
\usepackage[empty]{fullpage}
\usepackage[margin=0.5in]{geometry} % Sets 0.5 inch margins
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}

% Clear formatting for sections
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\huge Jane Doe} \\ \vspace{5pt}
    \small 
    (555) 111-6666 $|$ 
    \href{mailto:nameXYZ@example.com}{nameXYZ@example.com} $|$ 
    \href{https://linkedin.com}{://linkedin.com} $|$ 
    \href{https://github.com}{://github.com}
\end{center}


%---------- EDUCATION ----------
\section{Education}
  \begin{itemize}[leftmargin=*]
    \item[]
      \textbf{University of Maine} \hfill Orono, ME \\
      \textit{Bachelor of Science in Computer Science} \hfill \textit{May 2026} \\
      \small{GPA: 3.8/4.0 $|$ Relevant Coursework: Data Structures, Algorithms, Software Engineering}
  \end{itemize}


%---------- SKILLS ----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, C++, SQL, JavaScript \\
     \textbf{Frameworks:} React, Node.js, Django, Spring Boot \\
     \textbf{Tools:} Git, Docker, AWS, PostgreSQL, VS Code
    }}
 \end{itemize}


%---------- EXPERIENCE ----------
\section{Experience}
  \begin{itemize}[leftmargin=*]
    \item[]
      \textbf{Tech Solutions Inc.} \hfill Boston, MA \\
      \textit{Software Engineering Intern} \hfill \textit{June 2025 - August 2025}
      \begin{itemize}
        \item Developed and maintained microservices using Java and Spring Boot, improving API response time by 15\%.
        \item Collaborated with the QA team to write automated unit tests, covering 90\% of new feature code.
        \item Implemented CI/CD pipelines using GitHub Actions to streamline deployment processes.
      \end{itemize}
      
    \item[]
      \textbf{University of Maine IT Dept.} \hfill Orono, ME \\
      \textit{Student Developer} \hfill \textit{September 2023 - May 2025}
      \begin{itemize}
        \item Designed a responsive dashboard using React and Node.js for 5,000+ students to track campus events.
        \item Optimized database queries in PostgreSQL, reducing data retrieval time for legacy systems.
      \end{itemize}
  \end{itemize}


%---------- PROJECTS ----------
\section{Projects}
  \begin{itemize}[leftmargin=*]
    \item[]
      \textbf{EcoTrack} \textbar{} \small{\textit{React, Python, REST API}} \hfill \textit{January 2026}
      \begin{itemize}
        \item Built a full-stack web application that allows users to track and analyze their daily carbon footprint.
        \item Integrated a third-party REST API to provide real-time suggestions for sustainable commuting.
      \end{itemize}
      
    \item[]
      \textbf{Pathfinder} \textbar{} \small{\textit{Java, JavaFX, Dijkstra's Algorithm}} \hfill \textit{October 2024}
      \begin{itemize}
        \item Created an interactive desktop application that visualizes pathfinding algorithms on campus maps.
        \item Implemented Dijkstra's algorithm from scratch, allowing users to find the shortest route between buildings.
      \end{itemize}
  \end{itemize}

\end{document}